A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-21 manuscript.Rmd
grammerly

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For a priori planned analysis, preregistration should reduce "researcher degrees of freedom" therefore the number of decisions researcher can make that could unduly influence the results.
Preregistrations, however, have a problem.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
The structure these templates provides can more effectively reduce researchers degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
But these templates can not remove researchers degrees of freedoms completely, because it is impossible to verbally describe every detail of an analysis for all but the simplest analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write the code to conduct the analysis before you gather data.
We term this approach of writing and publishing code before data collection *preregistration as code (PAC)*.
PAC has the potential to all but eliminate researchers degrees of freedom that standard preregistration despite the best efforts afford.

The idea of submitting code as part of a preregistration is not new.
A prominent preregistration platform, [The Open Science Framework](https://osf.io/), suggests submitting scripts alongside the preregistration of methods.
In an informal literature search (we skimmed the first 300 results with the keywords `("pre registration"|"pre-registration"|preregistration)&(code|script|matlab|python|"R")`) we have found close to a dozen published articles which did included some form of script as part of their preregistration.

@@

First, preregistrations are plagued by non-reproducibility like any other research outcome.
@bakkerRecommendationsPreregistrationsInternal2020 found that, among the 210 preregistrations they investigated, 174 (67%) included a formal power analysis but from these only 34 (20%) provided enough information to reproduce the power analysis.
Even researcher who have gone to great length in submitting a script in their preregistration sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).

@@

Leaving meta-scientific benefits aside, a preregistration is a tool for planning a study.
To use PAC for study planing, we suggest that researchers write a dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
To that end, they should borrow from widely employed standards for writing an empirical manuscript [e.g. @apa7].
Then they should translate their method section into executable computer code and simulate data that has the same structure as the data they expect to obtain from their experiments.

@@

Describing the preregistration in form of a journal article requires authors to follow the same standards that also ensure that research articles are comprehensive enough to replicate the described study.
One particular advantage is the strong foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless it can be fruitful to consult preregistration templates, because of there strong focus on formulating a comprehensive methods section.

Another factor that ensures a comprehensive plan is writing the analysis based on simulated data.
While rather uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.
Simulating data forces the researcher to think about and address data analytic problems on a conceptual level before they make the effort to acquire data [@axelrodAdvancingArtSimulation1997].
It also affords researchers with a simple technical check whether the analysis code runs without failure [@braiekTestingMachineLearning2020] (for example, does the code work with missing values, extreme outliers, etc.).
Writing incomplete code is technically impossible or at least researchers would notice if they e.g. forgot to aggregate the data etc.

@@

With simulated data researchers can check if the analysis is technically complete and can also recover the true parameters of the simulation.
When an analysis fails to recover the correct values in idealized conditions with big samples researchers should not expect this analysis to work under realistic conditions.
Because the simulation captures the researchers expectations about the real world conditions it is the best way to assess the effectiveness of the analysis without actually gathering the data.

@@

A single simulated or synthesized dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researcher navigate several trade offs regarding their resources.
In the simplest case they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision]. @bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis does not necessarily increase the planned sample size. You may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

@@

To write a PAC researchers should start by drafting a manuscript in form of an R Markdown.
When they have completed the method section, they should begin writing code.
We suggest writing three functions for each hypothesis, one for the planned analysis, one for the simulating the data and one for reporting the results.
At the heart of a PAC lies the planned analysis so researchers should first draft a function called `planned_analysis()` that captures the description in the method section.
This function should receive the data and derive relevant results from it.

```{r}
planned_analyis <- function(data){
  # 1. preprocess e.g. with `rowMeans(data)`
  # 2. conduct analysis e.g. with `t.test()`
  # 3. `return(results)`
}
```

Because it is difficult to draft such function without interactively test it, researcher should than proceed to write a function for simulating data.

```{r}
simulate_data <- function(n, effect_size){
  # 1. warn users that the results are "fake"
  # 2. draw `n` samples with `effect_size`
  # 3. format and return in expected data format
}
```

As soon as they have written `planned_anaylsis()` and `simulate_data()` they can iteratively improve both functions, e.g. till `planned_analysis()` runs without error and recovers the correct parameters from `simulate_data()`.
The goal is that the output of `simulate_data()` works as input to the function `planned_analysis()`.

This process can be tedious and complicated.
If it proofs infeasible to simulate data, researcher can delay their preregistration till they have gathered data and repurpose the actual data.
Of course researcher must not analyze the data before they write the preregistration but they can obfuscate the real data by shuffling the dependent variable or otherwise create synthetic data that allows them to test the function `planned_analysis()` without actually revealing the research outcomes.

When the researchers are satisfied with the function `planned_analysis()` they can think about how they would like to report the results of the analysis, via tables, plots and text.
The implementation of this reporting should be in the function `report_analysis()`.

```{r}
report_results <- function(results){
  # 1. create markdown tables from results
  # 2. conditionally interpret results e.g. if(p < .025)"Result is significant."
  # (optional) visualize results
  # 3. return results section formatted in markdown
}
```

These function again should be accept the output of `planned_analysis()` as input.
The output of this function should be formatted in Markdown.
A variety of packages automatically generate well formatted outputs of statistical reports or even entire tables of estimates or figures directly from R objects.
Packages like [`pander`](https://github.com/Rapporter/pander) [@pander], [`stargazer`](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf) [@stargazer], [`apaTables`](https://dstanley4.github.io/apaTables/articles/apaTables.html) [@apaTables] and [`papaja`](http://frederikaust.com/papaja_man/) [@papaja] help you to create dynamically generated professional looking results.
The package [`report`](https://github.com/easystats/report) [@report] is particularly noteworthy because it not only generates tables, but also a simple interpretation of the effects as actual prose (e.g it quantifies the size of an effect).

Ideally, these three functions can be composed to create a "fake" results section, e.g. when composed to `report_analysis(planned_analysis(simulate_data()))` or `simulate_data() %>% planned_analysis() %>% report_analysis()` outputs a results section.

To summarize researchers write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as preregistration.
After they gathered the actual data, they replace the simulated data, run `planned_analysis()` and write the discussion.

# Preregistration as Code --- a Tutorial

To guide the reader through a preregistration as code (PAC), we will use an exemplary research question that was based on openly available data and merely chosen for simplicity of illustration:

> "Is there a mean difference in the personality trait 'Machiavellism' between self identified females and males?"

This example serves only didactic purposes and not to derive substantive claims.
Nevertheless, everything else is kept as close to a real research question as possible.

At the heart of a PAC lies the planned analysis.
We suggest writing a main analysis function that captures the full process of testing a research question.
This function receives a dataset as input and performs all statistical processing. <!--AB say anything about its output? is the Markdown the output?-->
For the hypothetical research question, we could for example plan to conduct a simple Student's t-test [@studentProbableErrorMean1908] with Welch's correction [@welchGeneralizationStudentProblem1947] an the average of machiavellism items of the Short Dard Triad [SD3, @Jones2013] between the binary-coded gender groups.
As an example of a data-dependent decision, we included a rank transformation if the skewness was greater than 1, converting the t-test to a supposedly more robust Mann–Whitney–Wilcoxon test.[^caution-mww]

[^caution-mww]: The Mann–Whitney–Wilcoxon is in fact **not** more robust than the Welch corrected t-test for reasonably large sample sizes. The interested reader can use the provided code for the simulation to verify that the t-test provides unbiased effect sizes but the Mann–Whitney–Wilcoxon overestimates effect size with increasing sample size and skewness.

This function is one possible translation of the verbal description above:

@@

Importantly, natural language descriptions do not map unambiguously onto computer code implementations. 
The same textual descriptions may be implemented differently by different persons depending on their statistical and programming knowledge but also based on their own expectations and beliefs.
One example would be using the function `wilcox.test` instead of the combinations of `rank` and `t.test`.
Both are valid implementation of the Mann–Whitney–Wilcoxon test but the first assumes equal variance whereas the second applies Welch's correction and hence is robust even with unequal variances across groups [@zimmermanRankTransformationsPower1993].
Mentioning every such minute implementation detail is almost impossible and would result in overly verbose preregistrations.
Still, these details can make a difference and provide unwanted researcher degrees-of-freedom.

<!--AB here is kind of a break in the text-->
To use this function one needs a compatible dataset. <!--AB what is "this" function? What does "compatible" mean?-->
At the time of preregistration there is of course no actual data available.
We therefore simulate a dataset first that resembles the expected structure of the empirical data that we will use for the final analysis.
Using the simulated dataset as placeholder, we can now write a scientific report including all analysis code blocks and the presentation of results, which can serve as PAC.
The following code simulates a dataset with one observed variable in two groups.

```{r simulate_data}
```
<!--AB it is odd that the return variable is called effect because it is a dataset-->

Here, we decided to randomly draw non-normal data to test how well our procedure performed under non-optimal situations.
Specifically, we draw from a $\chi^2$-distribution, where in one group we add difference that conforms to a given standardized effect size (a Cohen's d of .2).
This simulated dataset fits perfectly into our planned analysis with a sample size of 400 and 10 items: <!--AB in what way? please explain-->

***

```{r}
set.seed(112358) # fix state of RNG
results <- 
  planned_analysis(
    simulate_data(
      n = 400,# Sample size
      df = 8, # Chisq with DF = 8 has skewness = 1
      d = .2, # Cohen's D
      i = 10  # Number of items (should not effect anything)
    )
  )
```

Next, we add dynamic code blocks to our Markdown report that implement the planned reporting of the final results.
A variety of packages automatically generate well formatted outputs of statistical reports or even entire tables of estimates or figures directly from R objects.
Packages like [`pander`](https://github.com/Rapporter/pander) [@pander], [`stargazer`](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf) [@stargazer], [`apaTables`](https://dstanley4.github.io/apaTables/articles/apaTables.html) [@apaTables] and [`papaja`](http://frederikaust.com/papaja_man/) [@papaja] help you to create dynamically generated professional looking results.
The package [`report`](https://github.com/easystats/report) [@report] is particularly noteworthy because it not only generates tables, but also a simple interpretation of the effects as actual prose (e.g it quantifies the size of an effect).
Here we use the `report` package to create a preview of how our reporting will look like based on simulated data:<!--AB add citation to the report package-->

```{r, results='asis', eval=FALSE}
report::report(results$test)
```

This call to the `report()` function will yield the following automatically generated output:

```{r, results='asis', echo=FALSE}
report::report(results$test)
```
<!--AB it is difficult to discern the automatically generated text and out manuscript text even though there is the horizontal line. Not sure how to improve this.-->
***

@@

To determine a minimal sample size for this study we repeat this simulation across several combination of effect sizes and sample sizes.
One standard recomendations for choosing a sample size is to have an expected power of 80% based on the expected effect size.
@Jones2013 found in three studies gender differences of .24, .29, and .35 for their machiavilism subscale.
If we want to detect an effect of size `r choosen_d` with an `r choosen_power*100`% probability, our simulation shows that we require at least `r minn$n` participants.

<!--AB please add a figure number and a proper citation to the figure. Also, tell people where they can find the code to run the power analysis themselves-->

```{r, echo=FALSE}
res %>%
  ggplot(aes(n, power, color = d, group = d)) +
  geom_line() +
  geom_point(
    data = minn,
    size = 3,
    color = "black",
    shape = 3
  ) +
  theme_minimal() +
  scale_color_viridis_c() +
  theme(legend.title = element_text()) +
  labs(y = "Power\n(Proportion of significant results)",
       x = "Sample size",
       color = "Cohen's D") +
  NULL
```

>>>>

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For a priori planned analyses, preregistration should reduce "researcher degrees of freedom" therefore, the number of decisions researcher can make that could unduly influence the results.
Preregistrations, however, have a problem.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration is comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
The structure these templates provide can more effectively reduce researchers degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
Nevertheless, these templates can not remove researchers' degrees of freedom because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write the code to conduct the analysis before you gather data.
We term this writing and publishing code before data collection *preregistration as code (PAC)*.
PAC has the potential to all but eliminates researchers degrees of freedom that standard preregistration despite the best efforts afford.

The idea of submitting code as part of a preregistration is not new.
A prominent preregistration platform, [The Open Science Framework](https://osf.io/), suggests submitting scripts alongside the preregistration of methods.
In an informal literature search (we skimmed the first 300 results with the keywords `("pre registration"|"pre-registration"|preregistration)&(code|script|matlab|python|"R")`), we found close to a dozen published articles that included some form of script as part of their preregistration.

@@

First, preregistrations are plagued by non-reproducibility like any other research outcome.
@bakkerRecommendationsPreregistrationsInternal2020 found that, among the 210 preregistrations they investigated, 174 (67%) included a formal power analysis, but from these, only 34 (20%) provided enough information to reproduce the power analysis.
Even researchers who have gone to great lengths in submitting a script in their preregistration sometimes inexplicably fail to reproduce their results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).

@@

When leaving meta-scientific benefits aside, a preregistration is a tool for planning a study.
To use PAC for study planning, we suggest that researchers write a dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
To that end, they should borrow from widely employed standards for writing an empirical manuscript [e.g. @apa7].
Then they should translate their method section into executable computer code and simulate data that has the same structure as the data they expect to obtain from their experiments.

@@

Describing the preregistration in form of a journal article requires authors to follow the same standards that also ensure that research articles are comprehensive enough to replicate the described study.
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.

Another factor that ensures a comprehensive plan is writing the analysis based on simulated data.
While relatively uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.
When simulating data, researchers have to think about and address data-analytic problems on a conceptual level before making an effort to acquire data [@axelrodAdvancingArtSimulation1997].
It also affords researchers with a simple technical check whether the analysis code runs without failure [@braiekTestingMachineLearning2020] (for example, does the code work with missing values, extreme outliers, etc.).
Writing incomplete code is technically impossible, or at least researchers would notice if they, e.g. forgot to aggregate the data, and so forth.

@@

With simulated data, researchers can check if the analysis recovers the known parameters of the simulation.
When an analysis fails to recover the correct values in idealized conditions with big samples, researchers should not expect this analysis to be effective under realistic conditions.
Because the simulation captures the researchers' expectations about the real world, it is the best way to assess the effectiveness of the analysis without actually gathering the data.

@@

A single simulated dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researchers navigate several trade-offs regarding their resources.
In the simplest case, they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision].
@bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis does not necessarily increase the planned sample size.
Researchers may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

@@

To write a PAC, researchers should start by drafting a manuscript in the form of an R Markdown.
When they have completed the method section, they should begin writing code.
We suggest writing three functions for each hypothesis, one for the planned analysis, one for simulating the data and one for reporting the results.
At the heart of a PAC lies the planned analysis, so researchers should first draft a function called `planned_analysis()` that fits the description in their method section.
This function should receive the data and derive relevant results from it.

```{r, eval=FALSE}
planned_analyis <- function(data){
  # 1. preprocess e.g. with `rowMeans(data)`
  # 2. conduct analysis e.g. with `t.test()`
  # 3. `return(results)`
}
```

Because it is difficult to draft such a function without interactively testing it, the researcher should then write a function for simulating data.

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  # 1. warn users that the results are mocked
  # 2. draw `n` samples with `effect_size`
  # 3. format and return in expected data format
}
```

As soon as they have written a first draft of `planned_anaylsis()` and `simulate_data()` they can interactively improve both functions, e.g. till `planned_analysis()` runs without error and recovers the correct parameters from `simulate_data()`.
The goal is that the output of `simulate_data()` works as input to the function `planned_analysis()`.

This process can be tedious and complicated.
If it proves infeasible to simulate data, researcher can delay their preregistration till they have gathered data and repurpose the actual data.
Of course, researchers must not analyze the data before they write the preregistration.
However, they can obfuscate the real data by shuffling the dependent variable or otherwise create synthetic data that allows them to test the function `planned_analysis()` without actually revealing the research outcomes.

When the researchers are satisfied with the function `planned_analysis()`, they can think about how they would like to report the analysis results via tables, plots, and text.
The implementation of this reporting should be in the function `report_analysis()`.

```{r, eval=FALSE}
report_results <- function(results){
  # 1. create markdown tables from results
  # 2. conditionally interpret results e.g. if(p < .025)"Result is significant."
  # (optional) visualize results
  # 3. return results section formatted in markdown
}
```

This function should again accept the output of `planned_analysis()` as input.
The output of this function should be formatted in Markdown.
Various packages automatically generate well-formatted Markdown outputs of statistical reports or even entire tables of estimates or figures directly from R objects.
Packages like [`pander`](https://github.com/Rapporter/pander) [@pander], [`stargazer`](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf) [@stargazer], [`apaTables`](https://dstanley4.github.io/apaTables/articles/apaTables.html) [@apaTables] and [`papaja`](http://frederikaust.com/papaja_man/) [@papaja] help you to create dynamically generated professional looking results.
The package [`report`](https://github.com/easystats/report) [@report] is particularly noteworthy because it generates not only tables but also a straightforward interpretation of the effects as actual prose (e.g. it quantifies the size of an effect).

Ideally, these three functions can be composed to create a mock results section, e.g. when composed to `report_analysis(planned_analysis(simulate_data()))` or `simulate_data() %>% planned_analysis() %>% report_analysis()` they output a full results section.

To summarize, researchers write three functions, `planned_analysis()`, `simulate_data()`, and `report_analysis()` and embed these into a manuscript that serves as preregistration.
After they gathered the actual data, they replace the simulated data, render the dynamic manuscript (therefore run `planned_analysis()`) and write the discussion.

## An example of Preregistration as Code

We have made the argument that PAC has significant advantages over classical preregistration and have outlined how to implement PAC, but can PAC work in practice?
To answer this question and help researchers implementing PAC themselves, we have conducted a PAC that can serve as an example.
We will use an exemplary research question that was based on openly available data and merely chosen for simplicity of illustration:

> "Is there a mean difference in the personality trait 'Machiavellism' between self-identified females and males?"

Again, we propose a preregistration format that closely resembles a classical journal article, but that utilizes simulated data and dynamic document generation to serve simultaneously as preregistration and final manuscript.
The complete example is available in the (https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd).
In this section, we show excerpts of this example formatted in light grey and provide some commentary.

```{r, echo=FALSE}
show <- function(x, wrap = TRUE, cat = TRUE, fence = TRUE){
  stopifnot(length(x) == 1L)
  if(wrap)x <- str_c(str_wrap(str_split(x, "\\n\\n")[[1]]), collapse = "\n\n")
  if(!isFALSE(fence)){
    if(isTRUE(fence))fence <- "markdown"
    fence <- str_c("````", fence)
    x <-
      str_c(fence,
            x,
            "````",
            sep = "\n",
            collapse = "\n")
  }
  if(cat){
    cat(x)
    return(invisible(x))
  } else {
    return(x)
  }
}
show_prereg <-
  function(section,
           file = "preregistration.Rmd",
           wrap = TRUE,
           cat = TRUE,
           fence = TRUE) {
    prereg <- readr::read_lines(here::here(file))
    start <- stringr::str_c("<!--begin-", section, "-->")
    end <- stringr::str_c("<!--end-", section, "-->")
    start_pos <- which(prereg == start)
    end_pos <- which(prereg == end)
    if (length(start_pos) != 1L || length(end_pos) != 1L)
      stop("No section '", section, "' found.")
    excerpt <-
      str_c(prereg[(start_pos + 1):(end_pos - 1)], collapse = "\n")
    show(excerpt, wrap = wrap, cat = cat, fence = fence)
  }
```

As usual, researchers state why they are interested in their research question in the section "Introduction" and provide the necessary information and literature to understand the rest of the paper.
This example is drastically shortened for illustration purposes:

```{r, echo=FALSE, results='asis'}
show_prereg("theory")
```

After researchers have provided the research question, they proceed to explain how they want to study it.
For simplicity, we will use already published data that we have not yet analyzed:

```{r, echo=FALSE, results='asis'}
show_prereg("method")
```

We choose the following statistical procedure because many researchers may be familiar with it[^caution-mww]:

```{r, echo=FALSE, results='asis'}
show_prereg("ttest")
```

[^caution-mww]: The Mann–Whitney–Wilcoxon is in fact **not** more robust than the Welch corrected t-test for reasonably large sample sizes. The interested reader can use the [provided code for the simulation](https://github.com/aaronpeikert/repro-tutorial/blob/main/simulation.R) to verify that the t-test provides unbiased effect sizes but the Mann–Whitney–Wilcoxon overestimates effect size with increasing sample size and skewness.

We then translated this methods section into the following `planned_analysis()` function:

@@

This function illustrates two advantages of PAC.
First, a PAC can easily include data-dependent decisions creating different branches of analysis under different conditions.
Second, it highlights how difficult it is to describe a statistical analysis precisely.
The same verbal descriptions may be implemented differently by different persons depending on their statistical and programming knowledge and their expectations and beliefs.
One example would be using the function `wilcox.test` instead of the combinations of `rank` and `t.test`.
Both are valid implementations of the Mann–Whitney–Wilcoxon test, but the first assumes equal variance.
In contrast, the second applies Welch's correction and hence is robust even with unequal variances across groups [@zimmermanRankTransformationsPower1993].
Mentioning every such minute implementation detail is almost impossible and would result in overly verbose preregistrations.
Still, these details can make a difference and provide unwanted researchers' degrees of freedom.

The function `planned_analysis()` together with the function `simulate_data()` (not shown here) can be used to justify the planned sample size.
To that end, `simulate_data()` is repeatedly called with increased sample size and the proportion of significant results (power) is recorded.
The results for such a Monte Carlo simulation for this example are visualized in figure \@ref(fig:power).
The code for this power analysis can be found in the [online supplementary material](https://github.com/aaronpeikert/repro-tutorial/blob/main/simulation.R).

Monte Carlo simulations are, of course, not only applicable for this analysis method and also allow researchers to investigate other relevant properties of their analysis method beyond power [@brandmaier2018precision; @harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

@@

```{r, include=FALSE}
fig_caption <- str_c("Results of simulation for the power analysis. The cross indicates the sample size that archives ", choosen_power*100, "% assuming a Cohen's D of ", choosen_d, ".")
```

```{r power, echo=FALSE, fig.cap=fig_caption}
res %>%
  ggplot(aes(n, power, color = d, group = d)) +
  geom_line() +
  geom_point(
    data = minn,
    size = 3,
    color = "black",
    shape = 3
  ) +
  theme_minimal() +
  scale_color_viridis_c() +
  theme(legend.title = element_text()) +
  labs(y = "Power\n(Proportion of significant results)",
       x = "Sample size",
       color = "Cohen's D") +
  NULL
```

```{r, echo=FALSE, results='asis'}
show_prereg("power-code", wrap = FALSE)
```

```{r, echo=FALSE, results='asis'}
show_prereg("power")
```

We implemented a mechanism that only uses simulated data when the actual data is not yet available for the results section.
This mechanism also warns readers if these results are based on simulated data.
As soon as the actual data are available, the simulated data is no longer used, and the results represent the actual empirical results of the study.

```{r, echo=FALSE, results='asis'}
show_prereg("results", wrap = FALSE)
```

The last thing we need to do is to report our results with the combination of `planned_analysis()` and `report_analysis()`.

```{r, echo=FALSE, results='asis'}
show_prereg("report", wrap = FALSE)
```

This is an example of how the results could be reported (based on simulated data):

```{r, echo=FALSE, results='asis'}
set.seed(1234)
show(report_analysis(planned_analysis(simulate_data(900, 8, 0.3, 10)), cat = FALSE), fence = "")
```

The interested reader can find the example rendered with actual data in the [online supplementary material](this link does not work) and can view the changes we made since preregistering it on this [GitHub page](this link does not work).
